\documentclass[final]{ubb_dolgozat}
\usepackage{definitions}
\usepackage{url}
\sloppy
\frenchspacing

\lstloadlanguages{Java}

\lstset{language=Java}

\submityear{
2016
}
\submitmonthHU{
Július
}
\submitmonthRO{
Iulie
}
\submitmonthEN{
July
}

\titleHU{
Kontroll és egyensúlyozás -- alkalmazás Lego robotnál
}

\titleEN{
Control and balancing -- applied to Lego robots
}

\titleRO{
Control \c{s}i echilibrare -- aplicat la robo\c{t}i Lego
}

\author{
Márton Zete-Örs
}

\tutorHU{
dr. Jakab Hunor,\newline egyetemi adjunktus\\
}
\tutorRO{
Lector dr. Hunor Jakab\\
}
\tutorEN{
Assist prof. dr. Hunor Jakab
}

\begin{document}

\begin{abstractEN}
	
The thesis’ goal is to accomplish the remote control of  a MINDSTORMS EV3 two wheeled self balancing robot. The control framework is based on  network  communication between a mobile application and the robot itself. To achieve this goal there are two main components that need to be designed and implemented. Firstly the mobile application that needs to make the communication with the robot, and secondly an algorithm which makes the balancing of the robot possible.

The application and the algorithm which handles the balancing were written in Java. The EV3 control unit is responsible for navigating the robot with the help of the leJOS Linux based operating system. The robot remains in a balanced position by using a PID controller and a one-axis gyroscope sensor. For it to remain in a stable  state, its velocity, tilt angle and angular velocity need to approximate zero. Also if it were to remain in a standing balanced position without translation its position needs to approximate zero too.The PID’s input argument is the error variable which is the difference between the expected value and the current value of the sensor mearurements. In our case we need to minimize this error in order to not lose  balance. In conclusion the error is made up of four components: the robots tilt angle, angular velocity, velocity and position. By properly modifying these components we can manipulate the robot’s movement direction and velocity.The mobile application written for the Android platform, connects to the robot through the network and sends eligible commands to it. To accomplish and automate the connection between the two components we used the Cling UPnP library, which relies on the SSDP protocol for device and service discovery.

This work is the result of my own activity. I have neither given nor received unauthorized assistance on this work.
\vspace{-1cm}
\end{abstractEN}

\maketitle

{ \baselineskip 1ex
  \parskip 1ex
  \tableofcontents
}

\include{bevezeto}
\include{lego_robot}
\include{egyensulyozas}
\include{gyakorlat}
\include{kovetkeztetes}
\appendix

{ 
	\renewcommand{\baselinestretch}{1.4}\normalsize %
	\setlength{\itemsep}{-2.4mm}
	\setlength{\bibspacing}{0.67\baselineskip}
	\bibliographystyle{abbrvnat_hu}
	\bibliography{dolgozat}
}


\end{document}
